### 2019-09-04 README.Rmd
updates after meeting

- Paper
    - I reorganized my work into three repos and consolidated the journals
    - Can you re-explain your vision with the minipage format?
    - Sometimes LIME doesn't work on my computer anymore...
    - Read the locality paper in detail and added to journal
    - Updated LIME procedure and R package function notes
- Graphics Group
    - title and abstract
    - preview image
    - email list (should I be added as an admin?)
    - treats?

@@

- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
- add an assert_that statement in the code to check if the LIME package is changing
- point out differences and similarities from the other paper (such as normal sampling)
- code up Laugel et al's work
- read through papers giving an overview of the current explanation methods

>>>>

- Graphics Group
    - email list

@@

- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
- add an assert_that statement in the code to check if the LIME package is changing
- point out differences and similarities from the other paper (such as normal sampling)
- code up Laugel et al's work
- read through papers giving an overview of the current explanation methods
- check to see if there a paper showing how ridge regression is affected by sample size changes
- try fitting the ridge regression with the observed data only to see how it compares to the model fit with the ridge regression
